The document title

### 2021-04-02 manuscript/manuscript.Rmd
Add Acknowledgements section

>>>>

# Acknowledgments {.unnumbered}

This study was funded by the Foundation for Science and Technology of Portugal (FCT) (grant PTDC/DTP-DES/0968/2014) and by the European Regional Development Fund (ERDF) through the Operational Competitiveness Programme (COMPETE) (grant POCI-01-0145-FEDER-016707). The study was developed in the Research Centre in Physical Activity, Health and Leisure (CIAFEL) funded by ERDF through the COMPETE and by the FCT (grant UIDB/00617/2020). Lucas Veras was supported by the FCT (grant UI/BD/150673/2020), Florêncio Diniz-Sousa was supported by the FCT (grant SFRH/BD/117622/2016) and Giorjines Boppre was supported by the FCT (grant SFRH/BD/146976/2019). The authors thank the participants who took part in this research and all who have collaborated in the project.
